
\documentclass[11pt,article,oneside]{memoir}
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{setspace}

% margins
\usepackage[left=1.5in, right=1.75in, top=1in, bottom=0.75in]{geometry}% adjust the page margins

\RequirePackage{xcolor}
\definecolor{RiceBlue}{HTML}{00205B} % official Rice blue color -- use for text etc
\definecolor{RiceGray}{HTML}{7C7E7F} % official Rice gray -- use for Section
\definecolor{LightGray}{HTML}{E0E2E6} % background color -- do not use for anything else
\definecolor{BrickRed}{HTML}{C04829} % backup color 
\definecolor{GrassGreen}{HTML}{359245}
\definecolor{WarmYellow}{HTML}{E9A139}
%% Choose fonts for use with xelatex
\usepackage{fontspec}
\setmainfont[Path=fonts/,
Mapping={tex-text},
Numbers={OldStyle},
Ligatures={Common},
UprightFont=*-Regular,
BoldFont=*-Bold,
ItalicFont=*-Italic,
BoldItalicFont=*-BoldItalic
]{CrimsonText}
\setsansfont[Path=fonts/,
Mapping=tex-text,
Colour=b31b1b,
UprightFont=*-Regular,
BoldFont=*-Bold,
ItalicFont=*-Italic]{Lato}
\setmonofont[Path=fonts/,
Mapping=tex-text,
Scale=0.9,
UprightFont=*-Regular]{Inconsolata}

%%------------------------------------------------------------------------
%% Section styling
%%------------------------------------------------------------------------

%% This includes a fudge from the following link in order to get the
%% subsection to align with a section
%% http://tex.stackexchange.com/questions/19200/titlesec-remove-space-after-empty-margin-section

\makeatletter
\newif\ifaftersec\aftersecfalse

\newcommand\setsubskip{%
    \global\aftersectrue
    \everypar{%
        \global\aftersecfalse
        \if@noskipsec
            \global\@noskipsecfalse
            \clubpenalty\@M
            \hskip-\parindent
            \begingroup
                \@svsechd\unskip{\hspace{\@tempskipb}}%
            \endgroup
        \else
            \clubpenalty\@clubpenalty\everypar{}%
        \fi}}

\newcommand\subskip{%
  \ifaftersec
     \removelastskip%         EDIT 2
     \vspace{-\baselineskip}% EDIT 2 ??????????????
  \fi
  \global\aftersecfalse}

% Section styling
\titleformat{\section}[leftmargin]{\raggedleft\sffamily\bfseries\footnotesize}{}{0pt}{}[\setsubskip]
\titlespacing*{\section}{2cm}{1ex}{0.25in}

% Subsection styling
\titleformat{\subsection}{\subskip\itshape}{}{0pt}{}[]
\titlespacing*{\subsection}{0em}{2.5ex}{1ex}

\raggedbottom
\makeatother

% useful macro
\newcommand{\dotspace}{\quad}

% better lists
\usepackage{enumitem}
\setlist[itemize, 1]{nosep, noitemsep, labelsep=-5pt, leftmargin=*, after=\vspace{\baselineskip}, itemindent=-15pt, labelindent=5pt}

% Use BibLaTeX
\usepackage[autostyle=true, autopunct=true, english=american]{csquotes}
\usepackage[
	backend=biber,
	style=publist,
	plauthorfirstinit=true,
	plauthorhandling=highlight,
	plnumbered=false,
	labeldateparts=false,
	%linktitleall=true,
	boldyear=false,
	marginyear=false,
	doi=true,
	url=false,
	isbn=false,
	maxbibnames=99,
	maxcitenames=99,
  defernumbers,
  giveninits,
	date=year
]{biblatex}

\setlength{\bibhang}{15pt}

% add bib resources


\addbibresource{my-papers/my-papers.bib}


% include everything in bibliography
\nocite{*}

% bold my name
\plauthorname[James]{Doss-Gollin}

% make modifications to standard styles
\DeclareFieldFormat{title}{\mkbibquote{#1}}
\DeclareFieldFormat{url}{\url{#1}}
\DeclareFieldFormat[article]{pages}{#1}
\DeclareFieldFormat[inproceedings]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[incollection]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[article]{volume}{\mkbibbold{#1}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\DeclareFieldFormat[article]{url}{}
\DeclareFieldFormat{shorthandwidth}{#1}
\DeclareFieldFormat{extrayear}{}

% Remove In: for an article.
\renewbibmacro{in:}{%
  \ifentrytype{article}{}{%
  \printtext{\bibstring{in}\intitlepunct}}}

% Format sub-bibliography headings as subsections
\defbibheading{subbibliography}[\refname]{\subsection*{#1}}

%% other stuff
% icons for the contact info
\usepackage{fontawesome5}
\usepackage{academicons}

% macros and environments
\newcommand{\Header}[1]{\\\multicolumn{3}{L{7in}}{\color{BrickRed}\Large{\spacedlowsmallcaps{#1}}}\\}
\newcommand{\Publication}[1]{\fullcite{#1} & \citeyear{#1}}
\newcommand{\CVEntry}[3]{#1 & #2 & #3}
\newenvironment{cv}
{
	\noindent\begin{longtable}{ >{\em}R{1in} L{5in} >{\em}R{0.875in} }
}{
    \end{longtable}
}

% have to load this last
\usepackage{hyperref} % Required for adding links	and customizing them
%\hypersetup{colorlinks, breaklinks, urlcolor=RiceGray, linkcolor=RiceGray}
\hypersetup{colorlinks=false}

%---------------------------------------------------------------------

\begin{document}

%% Name and contact block

\begin{minipage}[t]{2.8in}
  \flushright {\footnotesize
    Rice University\\
    Department of Civil and Environmental Engineering\\
    6100 Main Street, Ryon Lab 204-MS 318\\ \vspace{0.01in}
    Houston, TX, 77005\\ \vspace{-0.04in}}
\end{minipage}%
\begin{minipage}[t]{2.5in}
  \flushright {\footnotesize  \texttt{\href{mailto:jdossgollin@rice.edu}{jdossgollin@rice.edu}} \, \faEnvelope} \\ \vspace{-0.21in}
  \flushright {\footnotesize  \texttt{\href{https://dossgollin-lab.github.io/}{https://dossgollin-lab.github.io/}} \, \faGlobe} \\ \vspace{-0.195in}
  \flushright {\footnotesize
    \texttt{\href{https://github.com/jdossgollin}{jdossgollin}} \, \faGithub} \\ \vspace{-0.185in}
  \flushright {\footnotesize
    \texttt{\href{https://scholar.google.com/citations?user=6ifLBBsAAAAJ}{James Doss-Gollin}} \, \aiGoogleScholar}

\end{minipage}

\bigskip

%% Name
\noindent{\LARGE\bfseries \textcolor{BrickRed}{James Doss-Gollin}}
\reversemarginpar

\bigskip

%% Research Interests

\section{research interests}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item Climate risk management and adaptation

  \item Decision-making under uncertainty

  \item Dynamics and spatiotemporal clustering of hydroclimate extremes

  \item Probabilistic modeling and uncertainty quantification

\end{itemize}

%% Appointments

\section{appointments}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item \textbf{Assistant Professor}, Department of Civil \& Environmental Engineering, Rice University, 2021--present

  \item \textbf{Postdoctoral Scholar}, Earth \& Environmental Systems Institute, Pennsylvania State University, 2020--2020

\end{itemize}

%% Education

\section{education}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item \textbf{Ph.D.}, Earth \& Environmental Engineering, Columbia University, 2020

  \item \textbf{M.S.}, Earth \& Environmental Engineering, Columbia University, 2016

  \item \textbf{B.S.}, Mechanical Engineering, Yale University, 2011

\end{itemize}

%% Awards

\section{awards}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item \textbf{Nickolas and Liliana Themelis Fellowship}, Fu Foundation School of Engineering and Applied Science, Columbia University. 2018

  \item \textbf{Graduate Research Fellowship, Climate and Large-Scale Atmospheric Dynamics}, National Science Foundation. 2017

  \item \textbf{Presidential Distinguished Fellowship}, Fu Foundation School of Engineering and Applied Science, Columbia University. 2015

  \item \textbf{Distinction in Major}, Department of Mechanical Engineering and Materials Science, Yale University. 2015

  \item \textbf{Legacy Award}, New Haven Promise. 2015

  \item \textbf{Larry Coben ’79 Fellowship}, Yale University. 2014

  \item \textbf{Vance-Carter Travel Award}, Yale University. 2013

  \item \textbf{Thomas C. Barry Travel Award}, Yale University. 2012

\end{itemize}

%% Publications
\section{publications}

\printbibliography[type=article, title={Peer-Reviewed Journal Articles}, heading=subbibliography]

\printbibliography[type=unpublished, title={Articles Under Review or Forthcoming}, heading=subbibliography]

\printbibliography[type=thesis, title={Dissertation}, heading=subbibliography]

\printbibliography[type=inproceedings, title={Conference Proceedings}, heading=subbibliography]

%% Invited Talks

\section{invited talks}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item \enquote{\textbf{Towards Adaptive Resilience: Decision and Policy Support for Household Flood Risk Management}}, Summer Seminar Series,  \textit{Columbia University Department of Earth and Environmental Engineering}. Remote. Aug. 2020.

  \item \enquote{\textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}}, Center for Climate Risk Management CLIMA Seminar,  \textit{the Pennsylvania State University}. State College, PA. Jan. 2020.

  \item \enquote{\textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}}, Department of Civil and Environmental Engineering Seminar,  \textit{Rice University}. Houston, TX. Jan. 2020.

  \item \enquote{\textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}}, Complex Systems Simulation and Optimization Group,  \textit{National Renewable Energy Laboratory}. Golden, CO. Jan. 2020.

  \item \enquote{\textbf{Drivers of Extreme Rainfall: Atmospheric Circulation Patterns and Regional Intense Rainfall in the Ohio River}}, European Flood Awareness System Group,  \textit{European Centre for Medium Range Weather Forecasting}. Reading, England. Sept. 2016.

  \item \enquote{\textbf{Understanding the Physical Drivers of Extreme Rainfall for Flood Prediction}}, Oxford Water Network,  \textit{Oxford University}. Oxford, England. Aug. 2016.

\end{itemize}

%% Workshops

\section{workshop presentations}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item \enquote{\textbf{Adaptive Resilience through Real Options and Deep Reinforecement Learning}}, Doctoral Consortium on Computational Sustainability,  \textit{Carnegie Mellon University}. Pittsburgh,  PA. Oral Presentation. Oct. 2019.

  \item \enquote{\textbf{Evaluating Staged Investments in Critical Infrastructure for Climate Adaptation}}, Interdisciplinary Ph.D. Workshop in Sustainable Development,  \textit{Columbia University}. New York, NY. Oral Presentation. Apr. 2019.

  \item \href{https://doi.org/10.6084/m9.figshare.8277002.v1}{\enquote{\textbf{Robust Adaptation to Multi-Scale Climate Variability}}}, The Nexus of Climate Data, Insurance, and Adaptive Capacity,  \textit{}. Asheville, NC. Poster Presentation. Nov. 2018.

  \item \href{https://doi.org/10.6084/m9.figshare.8277128.v2}{\enquote{\textbf{Extreme Rainfall in Paraguay during the 2015-16 Austral Summer: Causes and Predictive Skill}}}, North East Graduate Student Water Symposium,  \textit{University of Massachusetts Amherst}. Amherst, MA. Oral Presentation. Sept. 2017.

  \item \href{https://doi.org/10.6084/m9.figshare.8277167.v1}{\enquote{\textbf{Regional Intense Precipitation: Inferences From GCM Atmospheric Circulation Fields}}}, Modeling Research in the Cloud,  \textit{National Center for Atmospheric Research}. Boulder, CO. Poster Presentation. May 2017.

  \item \enquote{\textbf{Statistical-Dynamical Analysis of Climate Projections for Flood Infrastructure Design}}, Interdisciplinary Ph.D. Workshop in Sustainable Development 2017,  \textit{Columbia University}. New York, NY. Oral Presentation. Apr. 2017.

  \item \href{10.13140/RG.2.2.20146.30406}{\enquote{\textbf{Causes and Model Skill of the Persistent Intense Rainfall and Flooding in Paraguay during the Austral Summer 2015-2016}}}, Workshop on Subseasonal to Seasonal Predictability of Extreme Weather and Climate,  \textit{Columbia University}. New York, NY. Poster Presentation. Dec. 2016.

\end{itemize}

%% Grants and Contracts
%
%\section{grants and contracts}
%
%\mbox{}\vspace{-\dimexpr\baselineskip\relax}
%
%\begin{itemize}[label={}]
%  
%  \item Co-PI (PI: Klaus Keller at Penn State on subcontract from Battelle-Pacific Northwest National Laboratory). Department of Energy, Biological and Environmental Research. \enquote{Integrated Coastal Modeling (ICoM)}. \$1,200,000. 2019--2022.
%        
%  \item Co-PI (PI: Klaus Keller at Penn State on subcontract from Battelle-Pacific Northwest National Laboratory). Department of Energy, Biological and Environmental Research. \enquote{Integrated Multi-Scale Multi-Sector Modeling (IM3)}. \$25,000. 2019--2020.
%        
%\end{itemize}

%% Teaching

\section{teaching}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\vspace{\baselineskip}



\subsection{Columbia University}
\begin{itemize}[label={}]

  \item Environmental Data Analysis and Modeling. Teaching Assistant. Spring 2018.

\end{itemize}


%% Advising
%
%\section{advising}
%
%\mbox{}\vspace{-\dimexpr\baselineskip\relax}
%
%\vspace{\baselineskip}
%
%
%\subsection{Pennsylvania State University}
%\begin{itemize}[label={}]
%  
%  \item Carl Frederick Aquino, B.S. Geosciences. Co-advisor. 2019--2020.
%        
%\end{itemize}
%

%% Outreach

\section{outreach}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item Taught session on multi-objective robust decision-making, SCRiM Summer School. 2018, 2019.

\end{itemize}

%% Service

\section{service}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item Associate Deputy Editor, \emph{Climatic Change}.  2021--present.

  \item Co-Chair, MultiSector Dynamics Working Group on Uncertainty Quantification and Scenario Development. 2019--present.

  \item Member, MultiSector Dynamics Community of Practice Scientific Steering Group. 2019--present.

  \item Co-Convener and Co-Chair, AGU Session on MultiSector Dynamics: Science and Modeling for Societal Transformations II. 2020.

  \item Co-Guest Editor, \emph{Water}. Special Issue on 'Climate Model Projections: Sea-Level Rise and Impacts on Coastal Defense Decision-Making'. Forthcoming.

\end{itemize}

%% Professional Experience

\section{professional experience}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

  \item Research Assistant, Brownson Solar Research Group, Pennsylvania State University). 2011--2014

  \item Technical Editor, Journal of Modern Dynamics). 2008--2010

\end{itemize}



\end{document}