\documentclass[10pt,oneside]{article}

% language setup
\usepackage[english]{babel}

% margins - slightly increased top for header
\usepackage[left=0.75in, right=0.75in, top=1.25in, bottom=0.75in]{geometry}% adjust the page margins

\RequirePackage{xcolor}
\definecolor{RiceBlue}{HTML}{00205B} % official Rice blue color -- use for text etc
\definecolor{RiceGray}{HTML}{7C7E7F} % official Rice gray -- use for Section
\definecolor{LightGray}{HTML}{E0E2E6} % background color -- do not use for anything else
\definecolor{BrickRed}{HTML}{C04829} % backup color 
\definecolor{GrassGreen}{HTML}{359245}
\definecolor{WarmYellow}{HTML}{E9A139}
%% Choose fonts for use with xelatex


% Header and footer (skip first page)
\usepackage{fancyhdr}
\fancyhf{}
\fancyhead[L]{\footnotesize\textcolor{RiceGray}{James Doss-Gollin}}
\fancyhead[R]{\footnotesize\textcolor{RiceGray}{jdossgollin@rice.edu}}
\fancyfoot[L]{\footnotesize\textcolor{RiceGray}{updated \today}}
\fancyfoot[R]{\footnotesize\textcolor{RiceGray}{p. \thepage\ / \pageref{LastPage}}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\renewcommand{\headrule}{\color{RiceGray}\hrule width\headwidth height\headrulewidth \vskip-\headrulewidth}
\renewcommand{\footrule}{\color{RiceGray}\hrule width\headwidth height\footrulewidth \vskip-\footrulewidth}
\pagestyle{fancy}


\usepackage{fontspec}
\setromanfont[
  Path = ../fonts/,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
  Extension = .ttf,
]{Lato}
\setsansfont[
  Path = ../fonts/,
  UprightFont = *-Regular,
  Extension = .ttf,
]{Inconsolata}

% Section styling
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}
\titleformat{\subsubsection}{\normalsize\itshape}{}{0pt}{}

\titlespacing*{\section}{0pt}{1em}{0.5em}
\titlespacing*{\subsection}{0pt}{1em}{0pt}
\titlespacing*{\subsubsection}{0pt}{0pt}{0pt}

\raggedbottom

% useful macro
\newcommand{\dotspace}{\quad}

% Load longtable package
\usepackage{longtable}

% Custom environment for aligned entries with years
\newenvironment{alignedentries}[1][0pt]{%
  \noindent%
  \hspace{#1}%
  \begin{tabular*}{\dimexpr\textwidth-#1\relax}{@{}p{\dimexpr0.85\textwidth-#1\relax}@{\extracolsep{\fill}}r@{}}%
    }{%
  \end{tabular*}%
}
% Custom environment for aligned entries with hanging indent
\newenvironment{alignedentrieshang}[1][2em]{%
  \noindent%
}{%
}
\newcommand{\hangingitem}[2]{%
  \noindent%
  \begin{tabular*}{\textwidth}{@{}p{0.85\textwidth}@{\extracolsep{\fill}}r@{}}%
    \hangindent=2em \hangafter=1 #1 & #2%
  \end{tabular*}%
}
\newcommand{\entryitem}[2]{#1 & #2}
\newcommand{\entrybreak}{\\}

% better lists
\usepackage{enumitem}
\setlist[itemize, 1]{nosep, noitemsep, label={}, labelsep=-5pt, leftmargin=*, after=\vspace{\baselineskip}, itemindent=-15pt, labelindent=5pt}

% fixed width tables
\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\usepackage[autostyle=true, autopunct=true, english=american]{csquotes}
\usepackage[
  backend=biber,
  style=publist,
  plauthorfirstinit=true,
  plauthorhandling=highlight,
  plnumbered=false,
  labeldateparts=false,
  boldyear=true,
  marginyear=false,
  doi=true,
  url=false,
  isbn=false,
  maxbibnames=99,
  maxcitenames=99,
  date=year,
]{biblatex}
\setlength{\bibhang}{15pt}

% Force first name abbreviation for all authors in publist style
\ExecuteBibliographyOptions{giveninits=true}

\usepackage{amsmath}
% custom author highlighting: bold for James, blue+bold+dagger for group members
\renewcommand*{\plauthorhl}[1]{%
  \StrGobbleRight{#1}{1}[\trimmedname]%
  \IfSubStr{#1}{Doss-Gollin}%
  {\mkbibbold{\trimmedname}}%
  {\textcolor{RiceBlue}{\mkbibbold{\trimmedname$^\mathbf{\dagger}$}}}%
}

% bold my name (will be blue)
\plauthorname[James]{Doss-Gollin}

% highlight group members (will be purple with asterisk)
\plauthorname[Yuchen]{Lu}

% add bibliography resource
\addbibresource{my-papers.bib}

% include everything in bibliography
\nocite{*}

% Custom bibliography environment using alignedentrieshang
\defbibenvironment{hanging}
  {\begin{alignedentrieshang}}
  {\end{alignedentrieshang}}
  {}

% Custom bibliography drivers for hangingitem format
\DeclareBibliographyDriver{misc}{%
  \hangingitem{%
    \printnames{author}: \printfield[title]{title}. \printfield{journaltitle}%
    \iffieldundef{doi}{\iffieldundef{url}{}{. \printfield{url}}}{. \printfield{doi}}%
  }{---}%
  \entrybreak%
}

\DeclareBibliographyDriver{online}{%
  \hangingitem{%
    \printnames{author}: \printfield[title]{title}. \printfield{journaltitle}%
    \iffieldundef{doi}{\iffieldundef{url}{}{. \printfield{url}}}{. \printfield{doi}}%
  }{---}%
  \entrybreak%
}

\DeclareBibliographyDriver{article}{%
  \hangingitem{%
    \printnames{author}: \printfield[title]{title}. \printfield{journaltitle}%
    \iffieldundef{doi}{\iffieldundef{url}{}{. \printfield{url}}}{. \printfield{doi}}%
  }{\printfield{year}}%
  \entrybreak%
}

\DeclareBibliographyDriver{inproceedings}{%
  \hangingitem{%
    \printnames{author}: \printfield[title]{title}. \printfield{booktitle}%
    \iffieldundef{doi}{\iffieldundef{url}{}{. \printfield{url}}}{. \printfield{doi}}%
  }{\printfield{year}}%
  \entrybreak%
}

%% other stuff
% icons for the contact info
\usepackage{fontawesome5}
\usepackage{academicons}

% conditional logic for author highlighting
\usepackage{ifthen}
\usepackage{xstring}

% page reference for total page count
\usepackage{lastpage}

% have to load this last
\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{hidelinks, breaklinks}

%---------------------------------------------------------------------

\begin{document}
\reversemarginpar

\nocite{*}

\thispagestyle{empty}
%% Name and contact block
\noindent{
  \footnotesize
  \color{RiceGray}
  \begin{tabular*}{\textwidth}{@{}p{0.5\textwidth}@{\extracolsep{\fill}}r@{}}
    Rice University       & \texttt{\href{mailto:jdossgollin@rice.edu}{jdossgollin@rice.edu}} \, \faEnvelope                                                                                  \\
    Department of Civil and Environmental Engineering       & \texttt{\href{https://dossgollin-lab.github.io}{https://dossgollin-lab.github.io}} \, \faGlobe                                                                                                \\
    6100 Main Street, Ryon Lab 204-MS 318    & \texttt{\href{https://github.com/jdossgollin}{jdossgollin}} \, \faGithub                                                                      \\
    Houston, TX, 77005 & \texttt{\href{https://scholar.google.com/citations?user=6ifLBBsAAAAJ}{James Doss-Gollin}} \, \aiGoogleScholar \\
  \end{tabular*}
}

\bigskip

%% Name
\noindent{\LARGE\bfseries \textcolor{RiceBlue}{James Doss-Gollin}}




%% Appointments
\section{APPOINTMENTS}



\noindent\textbf{Rice University}

\begin{alignedentries}[2em]
\entryitem{\textit{Assistant Professor}, Department of Civil \& Environmental Engineering.}{2021---}\entrybreak
\end{alignedentries}


\noindent\textbf{The Pennsylvania State University}

\begin{alignedentries}[2em]
\entryitem{\textit{Postdoctoral Scholar}, Earth \& Environmental Systems Institute.}{2020}
\end{alignedentries}


%% Education
\section{EDUCATION}



\noindent\textbf{Columbia University}

\begin{alignedentries}[2em]

\entryitem{\textit{Ph.D. in Earth \& Environmental Engineering}.}{2020}\entrybreak

\entryitem{\textit{M.S. in Earth \& Environmental Engineering}.}{2016}

\end{alignedentries}


\noindent\textbf{Yale University}

\begin{alignedentries}[2em]

\entryitem{\textit{B.S. in Mechanical Engineering}.}{2015}

\end{alignedentries}


%% Awards
\section{AWARDS}

\begin{alignedentrieshang}

\hangingitem{\textbf{Outstanding Reviewer Award}, Earth's Future.}{2023}

\hangingitem{\textbf{Nickolas and Liliana Themelis Fellowship}, Fu Foundation School of Engineering and Applied Science, Columbia University.}{2018}

\hangingitem{\textbf{Graduate Research Fellowship, Climate and Large-Scale Atmospheric Dynamics}, National Science Foundation.}{2017}

\hangingitem{\textbf{Presidential Distinguished Fellowship}, Fu Foundation School of Engineering and Applied Science, Columbia University.}{2015}

\hangingitem{\textbf{Distinction in Major}, Department of Mechanical Engineering and Materials Science, Yale University.}{2015}

\hangingitem{\textbf{Legacy Award}, New Haven Promise.}{2015}

\hangingitem{\textbf{Larry Coben '79 Fellowship}, Yale University.}{2014}

\hangingitem{\textbf{Vance-Carter Travel Award}, Yale University.}{2013}

\hangingitem{\textbf{Thomas C. Barry Travel Award}, Yale University.}{2012}

\end{alignedentrieshang}


%% Grants and Contracts
\section{GRANTS AND CONTRACTS}

\textit{Amounts reflect Rice portion for collaborative grants and subawards; total amount for direct awards.}

\medskip

\begin{alignedentrieshang}

\hangingitem{\textit{National Science Foundation}\textit{: Confronting Hazards, Impacts and Risks for a Resilient Planet (CHIRRP)}. ``RAISE: Flood Resilience in Rural Texas Communities.'' \textbf{Co-PI} (Rice Lead: Avantika Gori) (PI: Avantika Gori). \textbf{\$999,986}.}{2025--2028}

\hangingitem{\textit{Consortium for Enhancing Resilience and Catastrophe Modeling (CERCAT)}. ``A Nonstationary Joint Probability Method for Tropical Cyclone Hazard Assessment.'' \textbf{Lead PI}. \textbf{\$75,000}.}{2025--2026}

\hangingitem{\textit{NVIDIA}. ``Computing Infrastructure for AI-enhanced Climate Risk and Resilience at Rice.'' \textbf{Co-PI} (PI: Arlei Lopes da Silva). \textbf{in-kind}.}{2025--2025}

\hangingitem{\textit{Rice University Sustainability Institute}. ``Workshop on Nature-Based Solutions for Resilient Coastal Cities.'' \textbf{Co-PI} (PI: Philip Bedient). \textbf{\$7,500}.}{2024--2025}

\hangingitem{\textit{Ken Kennedy Institute at Rice University}. ``Advancing AI for Climate Risk and Urban Resilience.'' \textbf{Lead PI}. \textbf{\$160,000}.}{2024--2025}

\hangingitem{\textit{National Science Foundation}. ``IUCRC Planning Grant Rice University: Center for Climate, Equity and Resilience in Catmodeling (CERCat).'' \textbf{Co-PI} (PI: Jamie Padgett). \textbf{\$20,000}.}{2024--2025}

\hangingitem{\textit{Texas Water Development Board}. ``Developing Future Rainfall Frequency Grids for the State of Texas.'' \textbf{Rice PI}. \textbf{\$77,750}. Subaward from Texas A\&M University (PI: John Nielsen-Gammon); \$192,828 total}{2022--2025}

\hangingitem{\textit{National Science Foundation}\textit{: Strengthening America's Infrastructure}. ``EAGER: Participatory Design for Water Quality Monitoring of Highly Decentralized Water Infrastructure Systems.'' \textbf{Rice PI} (PI: Alicia Cooperman). \textbf{\$104,684}.}{2022--2025}

\hangingitem{\textit{National Science Foundation}\textit{: Climate and Large-Scale Dynamics}. ``Collaborative Research: Evaluating the Past and Future of Mississippi River Hydroclimatology to Constrain Risk via Integrated Climate Modeling, Observations, and Reconstructions.'' \textbf{Co-PI} (Rice Lead: Sylvia Dee) (PI: Sylvia Dee). \textbf{\$472,024}.}{2022--2025}

\hangingitem{\textit{Rice University}\textit{: Sustainable Futures Fund}. ``Leveraging Earth System Observations at Multiple Scales to Improve Stormwater Management in Houston.'' \textbf{Lead PI}. \textbf{\$50,000}.}{2022--2023}

\hangingitem{\textit{100,000 Strong in the Americas Innovation Fund}. ``IFCE-Rice-SENAI Program on Artificial Intelligence for Urban Sustainability and Resilience to Natural Disasters in the Americas.'' \textbf{Co-PI} (PI: Arlei Lopes da Silva). \textbf{\$50,000}.}{2022--2023}

\hangingitem{\textit{Energy Foundation}. ``Synthesis of Texas Electricity Research from Rice University.'' \textbf{Co-PI} (PI: Daniel Cohan). \textbf{\$24,928}.}{2022--2023}

\end{alignedentrieshang}

%% Publications

\section{PUBLICATIONS}

{\textcolor{RiceBlue}{\textbf{$^\mathbf{\dagger}$ denotes Rice advisee publication}}}.
\href{https://scholar.google.com/citations?user=6ifLBBsAAAAJ}{Google Scholar \aiGoogleScholar} \textit{citations}: 568, \textit{h-index}: 11, \textit{i10-index}: 13.
\medskip

\defbibfilter{ispreprint}{%
    type=misc
    or type=online
}

\subsection{IN PREP. / UNDER REVIEW}

\printbibliography[filter=ispreprint, heading=none, env=hanging]

\subsection{JOURNAL ARTICLES}

\printbibliography[heading=none, type=article, env=hanging]

\subsection{PEER-REVIEWED CONFERENCE PAPERS}

\printbibliography[heading=none, type=inproceedings, env=hanging]

%% Invited Talks
\subsection{INVITED TALKS}

\begin{alignedentrieshang}

\hangingitem{Panelist. Exploring Water Resilience to Emerging Challenges,  \textbf{Society for Risk Analysis}, Remote Presentation.}{2024}

\hangingitem{\enquote{Advancing Urban Flood Risk Management through Physics-informed, Data-Driven Hazard Assessment}. Earth, Marine, and Environmental Science Seminar,  \textbf{University of North Carolina}, Chapel Hill, NC.}{2024}

\hangingitem{\enquote{Quantifying and Characterizing Uncertain Climate Hazards to Enable Adaptive Resilience}. Atmospheric Sciences Seminar,  \textbf{Texas A\&M University}, College Station, TX.}{2022}

\hangingitem{\enquote{Unprecedented Impacts Don't Require Unprecedented Weather}. Post-Harvey Climate \& Flood Impacts on the Built Environment,  \textbf{Severe Storm Prediction, Education, \& Evacuation from Disasters Center}, Houston, TX.}{2022}

\hangingitem{\enquote{Revisiting Our Design Criteria: What Hazards Should We Design for in a Changing Climate?}. Hydrologic Sciences and Water Resources Engineering Seminar,  \textbf{University of Colorado Boulder}, Remote Presentation.}{2022}

\hangingitem{\enquote{Adapting Engineering Design Criteria to a Changing Climate: Insights from House Elevation }. Technical Webinar,  \textbf{ASCE Central New Jersey Branch}, Remote Presentation.}{2022}

\hangingitem{Panelist. Extreme Weather: How To Report on a World That's Warmer, Colder, Wetter, Drier and Weirder,  \textbf{31st Annual Conference of the Society of Environmental Journalists}, Houston, TX.}{2022}

\hangingitem{\enquote{Predictable and Preventable: Lessons in Climate Risk Management from the Texas Coast (and Beyond)}. Climate Risk and Financial Institutions Seminar (Prof. Madison Condon),  \textbf{Boston University School of Law}, Remote Presentation.}{2022}

\hangingitem{\enquote{Extreme Impacts Don't Require Extreme Weather: Lessons from the February 2021 Texas Blackouts}. Outreach Event: Science is for Everyone,  \textbf{American Meteorological Society}, Remote Presentation.}{2022}

\hangingitem{\enquote{Extreme Impacts Don't Require Extreme Weather: Lessons from the February 2021 Texas Blackouts}. Compound Events Working Group,  \textbf{Risk KAN (Knowledge Action Networks)}, Remote Presentation.}{2021}

\hangingitem{Panelist. Tail events: Prediction, Planning, and Performance,  \textbf{Harvard Electricity Policy Group}, Remote Presentation.}{2021}

\hangingitem{\enquote{Towards Adaptive Resilience: Managing Flood Risks in a Changing World}. Technical Webinar,  \textbf{ASCE Central New Jersey Branch}, Remote Presentation.}{2021}

\hangingitem{\enquote{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}. Center for Climate Risk Management CLIMA Seminar,  \textbf{the Pennsylvania State University}, State College, PA.}{2020}

\hangingitem{\enquote{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}. Department of Civil and Environmental Engineering Seminar,  \textbf{Rice University}, Houston, TX.}{2020}

\hangingitem{\enquote{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}. Complex Systems Simulation and Optimization Group,  \textbf{National Renewable Energy Laboratory}, Golden, CO.}{2020}

\hangingitem{\enquote{Drivers of Extreme Rainfall: Atmospheric Circulation Patterns and Regional Intense Rainfall in the Ohio River}. European Flood Awareness System Group,  \textbf{European Centre for Medium Range Weather Forecasting}, Reading, England.}{2016}

\hangingitem{\enquote{Understanding the Physical Drivers of Extreme Rainfall for Flood Prediction}. Oxford Water Network,  \textbf{Oxford University}, Oxford, England.}{2016}

\end{alignedentrieshang}

%% WORKSHOPS
\subsection{CONFERENCE AND WORKSHOP PRESENTATIONS}

\medskip

\begin{alignedentrieshang}


\hangingitem{\enquote{Robust Trends in Extreme Rainfall Probabilities in Texas}. \textbf{2025 Texas Climate Conference}, \textit{Rice University and Texas A\&M University}, Houston, TX [\textit{Talk}].}{2025}



\hangingitem{\enquote{Use-Inspired Tools for Climate Hazard Assessment}. \textbf{Nature-Based Solutions for a Resilient Gulf Coast Workshop}, \textit{Rice University}, Houston, TX [\textit{Talk}].}{2025}



\hangingitem{\enquote{Advancing Urban Flood Hazard Characterization through Machine Learning: Challenges and Opportunities}. \textbf{American Geophysical Union Fall Meeting 2024}, Washington, DC [\textit{Talk}].}{2024}



\hangingitem{\textcolor{RiceBlue}{\textbf{Yuchen Lu}}$^\mathbf{\dagger}$: \enquote{TxRAIN-Observational: A Hierarchical Bayesian Spatial Framework to Assess Nonstationary Rainfall Intensity, Frequency, and Duration in Texas}. \textbf{American Geophysical Union Fall Meeting 2024}, Washington, DC [\textit{Talk}].}{2024}



\hangingitem{\enquote{Assessing and Managing Climate Risks to Electricity Systems in an Era of Climate Change and Energy Transition}. \textbf{American Geophysical Union Fall Meeting 2024}, Washington, DC [\textit{Talk}].}{2024}



\hangingitem{\textcolor{RiceBlue}{\textbf{Yuchen Lu}}$^\mathbf{\dagger}$: \enquote{Nonstationary Extreme Precipitation Probabilities in Texas}. \textbf{Fall Meeting}, \textit{Consortium for Enhancing Resilience and Catastrophe Modeling (CERCat)}, Bethlehem, PA [\textit{Poster}].}{2024}



\hangingitem{\enquote{Leveraging Machine Learning to Advance Urban Flood Hazard Assessment: Challenges and Opportunities}. \textbf{Data-driven and physics-based machine learning methods for forecasting and knowledge discovery of surface hydrology}, \textit{Conference on Computational Methods in Water Resources}, Tucson, AZ [\textit{Talk}].}{2024}



\hangingitem{\enquote{Incorporating Temperature Projections into Energy Systems Planning}. \textbf{Extreme Heat Workshop}, \textit{Columbia University}, New York, NY [\textit{Talk}].}{2024}



\hangingitem{\textcolor{RiceBlue}{\textbf{Yuchen Lu}}$^\mathbf{\dagger}$: \enquote{Spatially Varying and Duration Dependent Covariate Model: A Hierarchical Bayesian Framework for Multi-duration Extreme Precipitation Frequency Analysis in Texas}. \textbf{World Environmental \& Water Resources Congress 2024}, \textit{Environmental \& Water Resources Institute (EWRI) - ASCE}, Milwaukee, WI [\textit{Talk}].}{2024}



\hangingitem{\textcolor{RiceBlue}{\textbf{Yuchen Lu}}$^\mathbf{\dagger}$: \enquote{H21T-1602: Spatially Varying Covariate Model: A Hierarchical Bayesian Framework for Precipitation Frequency Analysis in the Gulf Coast}. \textbf{American Geophysical Union Fall Meeting 2023}, San Francisco, CA [\textit{Talk}].}{2023}



\hangingitem{\enquote{NH14B-07: Linking Robust Trends in Observations and Models to Develop Nonstationary Rainfall Frequency Grids for the State of Texas}. \textbf{American Geophysical Union Fall Meeting 2023}, San Francisco, CA [\textit{Talk}].}{2023}



\hangingitem{\enquote{A Bayesian Spatial Hierarchical Framework for Process-Informed Nonstationary Analysis of Precipitation Frequencies}. \textbf{13th International Workshop on Statistical Hydrology}, \textit{International Association of Hydrological Sciences}, Boston, MA [\textit{Talk}].}{2023}



\hangingitem{\textcolor{RiceBlue}{\textbf{Yuchen Lu}}$^\mathbf{\dagger}$: \enquote{H42E-1333: Nonstationary GEV with Hierarchical Spatial Pooling: A Spatiotemporal Bayesian Framework for Nonstationary Extreme Precipitation Frequency Analysis in the Gulf Coast}. \textbf{American Geophysical Union Fall Meeting 2022}, Chicago, IL [\textit{Talk}].}{2022}



\hangingitem{\enquote{H35F-07: Near-term Predictability Lowers Long-Term Adaptation Costs}. \textbf{American Geophysical Union Fall Meeting 2022}, Chicago, IL [\textit{Talk}].}{2022}



\hangingitem{\enquote{H25U-1265: Operationalizing Bayesian Model Checking for Robust Decision Making: Insights from House Elevation}. \textbf{American Geophysical Union Fall Meeting 2021}, New Orleans, LA [\textit{Poster}].}{2021}



\hangingitem{\enquote{A14H-03: How Unprecedented Was the February 2021 Texas Cold Snap?}. \textbf{American Geophysical Union Fall Meeting 2021}, New Orleans, LA [\textit{Talk}].}{2021}



\hangingitem{\enquote{Valuing Flexibility and Soft Instruments for Sequential Decision Problems}. \textbf{2020 Annual Meeting}, \textit{Society for Decision Making under Deep Uncertainty},  [\textit{Remote Presentation}].}{2020}



\hangingitem{\enquote{H11G-07: Towards Adaptive Resilience: Managing Uncertainties and Exploiting Predictability across Timescales}. \textbf{American Geophysical Union Fall Meeting 2019}, San Francisco, CA [\textit{Talk}].}{2019}



\hangingitem{\enquote{Adaptive Resilience through Real Options and Deep Reinforecement Learning}. \textbf{Doctoral Consortium on Computational Sustainability}, \textit{Carnegie Mellon University}, Pittsburgh,  PA [\textit{Talk}].}{2019}



\hangingitem{\enquote{Evaluating Staged Investments in Critical Infrastructure for Climate Adaptation}. \textbf{2019 Interdisciplinary Ph.D. Workshop in Sustainable Development}, \textit{Columbia University}, New York, NY [\textit{Talk}].}{2019}



\hangingitem{\enquote{H52F-05: Robust Adaptation to Cyclical Climate Risk}. \textbf{American Geophysical Union Fall Meeting 2018}, Washington, DC [\textit{Talk}].}{2018}



\hangingitem{\enquote{Robust Adaptation to Multi-Scale Climate Variability}. \textbf{The Nexus of Climate Data, Insurance, and Adaptive Capacity}, Asheville, NC [\textit{Poster}].}{2018}



\hangingitem{\enquote{A31H-0135: Causes and Model Skill of the Persistent Intense Rainfall and Flooding in Paraguay during the Austral Summer 2015-2016}. \textbf{American Geophysical Union Fall Meeting 2017}, New Orleans, LA [\textit{Talk}].}{2017}



\hangingitem{\enquote{H22B-02: Designing and Operating Infrastructure for Nonstationary Flood Risk Management}. \textbf{American Geophysical Union Fall Meeting 2017}, New Orleans, LA [\textit{Talk}].}{2017}



\hangingitem{\enquote{Extreme Rainfall in Paraguay during the 2015-16 Austral Summer: Causes and Predictive Skill}. \textbf{North East Graduate Student Water Symposium}, \textit{University of Massachusetts Amherst}, Amherst, MA [\textit{Talk}].}{2017}



\hangingitem{\enquote{Regional Intense Precipitation: Inferences From GCM Atmospheric Circulation Fields}. \textbf{Modeling Research in the Cloud}, \textit{National Center for Atmospheric Research}, Boulder, CO [\textit{Poster}].}{2017}



\hangingitem{\enquote{Statistical-Dynamical Analysis of Climate Projections for Flood Infrastructure Design}. \textbf{Interdisciplinary Ph.D. Workshop in Sustainable Development 2017}, \textit{Columbia University}, New York, NY [\textit{Talk}].}{2017}



\hangingitem{\enquote{Causes and Model Skill of the Persistent Intense Rainfall and Flooding in Paraguay during the Austral Summer 2015-2016}. \textbf{Workshop on Subseasonal to Seasonal Predictability of Extreme Weather and Climate}, \textit{Columbia University}, New York, NY [\textit{Poster}].}{2016}


\end{alignedentrieshang}

%% Media Coverage
\section{MEDIA HIGHLIGHTS}

\begin{alignedentrieshang}

\hangingitem{\enquote{Historic Texas Flooding.} \textbf{KEYE-AUS (CBS)} [\textit{recorded video interview}].}{2025}

\hangingitem{\enquote{Houston's Morning Show.} \textbf{Fox26 Houston} [\textit{live video interview}].}{2025}

\hangingitem{\enquote{Breaking down the force of water in the Texas floods.} \textbf{AP News} --- Michael Phillis [\textit{print}].}{2025}

\hangingitem{\enquote{Here are some things you can do to be better prepared for major flooding.} \textbf{Associated Press} --- Caleigh Wells [\textit{print}].}{2025}

\hangingitem{\enquote{ABC13-Luke Jones speaks with James Doss-Gollin, an assistant professor of Civil and Environmental Engineering at Rice University, about the key differences between flooding in Houston and central Texas..} \textbf{ABC13} --- Luke Jones [\textit{recorded video interview}].}{2025}

\hangingitem{\enquote{After deadly flooding in Central Texas, state lawmakers look to prevent similar tragedies.} \textbf{KVUE} --- Daniel Perreault [\textit{recorded video interview}].}{2025}

\hangingitem{\enquote{New Flood Warning System Greenlit Shortly Before Deadly Texas Disaster.} \textbf{The Wall Street Journal} --- Joseph De Avila [\textit{print}].}{2025}

\hangingitem{\enquote{Questions arise on how emergency warning systems work after Central Texas flood.} \textbf{ABC13} --- Tom Abrahams [\textit{print}].}{2025}

\hangingitem{\enquote{Bajo la Amenaza del Golfo (Under the Threat of the Gulf).} \textbf{Telemundo Houston} [\textit{recorded video interview}].}{2025}

\hangingitem{\enquote{Will Texas become too hot for humans?.} \textbf{BBC Future} --- Sarah Griffiths [\textit{print}].}{2023}

\hangingitem{\enquote{Climate change has sent temperatures soaring in Texas.} \textbf{The Texas Tribune} --- Erin Douglas, Yuriko Schumacher and Alex Ford [\textit{print}].}{2023}

\hangingitem{\enquote{Texas could have foreseen 2021 cold-wave disaster, new study concludes.} \textbf{Texas Climate News} --- Bob Henson [\textit{print}].}{2022}

\hangingitem{\enquote{Opinion: The risks of climate change are great - so are the rewards of solving it.} \textbf{Houston Chronicle} --- Andrew Dessler, James Doss-Gollin, and Katherine Hayhoe [\textit{print}].}{2021}

\hangingitem{\enquote{The False Comfort of Higher Seawalls.} \textbf{The New Republic} --- Paola Rosa-Aquino [\textit{print}].}{2019}

\hangingitem{\enquote{New Study Shows Promise for Long-Term Weather Forecasts in South America.} \textbf{State of the Planet} --- Elisabeth Gawthrop [\textit{print}].}{2018}

\end{alignedentrieshang}


%% Teaching
\section{TEACHING AND ADVISING}

\subsection{COURSES TAUGHT}


\begin{alignedentrieshang}

\hangingitem{Rice CEVE 543: \textit{Statistical-Physical Methods for Hydroclimate Extremes and Catastrophes}.}{Fall 2025}

\hangingitem{Rice CEVE 101: \textit{Fundamentals of Civil and Environmental Engineering}.}{Fall 2024}

\hangingitem{Rice CEVE 421/521: \textit{Climate Risk Management}.}{Spring 2024}

\hangingitem{Rice CEVE 543: \textit{Data Science Methods for Climate Hazard Assessment}.}{Fall 2023}

\hangingitem{Rice CEVE 421/521: \textit{Climate Risk Management}.}{Spring 2023}

\hangingitem{Rice CEVE 543: \textit{Environmental Data Science}.}{Spring 2022}

\hangingitem{Rice CEVE 101: \textit{Fundamentals of Civil and Environmental Engineering}.}{Fall 2021}

\end{alignedentrieshang}


%% Advising
\subsection{CURRENT GRADUATE STUDENTS}

\begin{alignedentrieshang}

\hangingitem{True Furrh: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. \textbf{Committee Member}.}{2021---}

\hangingitem{Dongwook Kim: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. \textbf{Primary Advisor}.}{2024---}

\hangingitem{Yuchen Lu: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. \textbf{Primary Advisor}.}{2021---}

\hangingitem{Kelsey Murphy: \textbf{Ph.D.} in Earth, Environmental, and Planetary Sciences, Rice University. \textbf{Committee Member}.}{2021---}

\hangingitem{Jonah Schaechter: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. \textbf{Primary Advisor}.}{2024---}

\hangingitem{Valeriia Sobolevskaia: \textbf{Ph.D.} in Earth, Environmental, and Planetary Sciences, Rice University. \textbf{Committee Member}.}{2020---}

\end{alignedentrieshang}

\subsection{PAST GRADUATE STUDENTS}

\begin{alignedentrieshang}

\hangingitem{Karan Jakhar: \textbf{Ph.D.} in Mechanical Engineering, Rice University. Thesis: \enquote{Equation Discovery and Deep Learning for Geophysical Turbulence}. \textbf{Committee Member}.}{2025}

\hangingitem{Kyle Ostlind: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Evaluating Runoff Response to Nature-Based Solutions under Varying Development Scenarios in Upper Cypress Creek near Houston, Texas}. \textbf{Committee Member}.}{2025}

\hangingitem{Katlyn Schmeltzer: \textbf{MCEE} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Pre-Trained Long Short-Term Memory Network Performance for Streamflow Prediction in the Brazos River Basin}. \textbf{Primary Advisor}.}{2025}

\hangingitem{John A. Baer: \textbf{M.S.} in Earth, Marine and Environmental Sciences, University of North Carolina at Chapel Hill. Thesis: \enquote{Quantifying Precipitation-Induced Uncertainty in Flood Hazard Assessment in a Coastal Urban Area}. \textbf{Committee Member}.}{2024}

\hangingitem{Kendall Capshaw: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Modeling Coastal Petrochemical Infrastructure Risk, Resilience, and Cascading Community Consequences}. \textbf{Committee Member}.}{2024}

\hangingitem{Xinyue Luo: \textbf{Ph.D.} in Earth, Environmental and Planetary Sciences, Rice University. Thesis: \enquote{Characterizing the El Niño-Southern Oscillation and Its North American Teleconnections over the Last Millennium}. \textbf{Committee Member}.}{2024}

\hangingitem{Anibal Tafur Gutierrez: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Methods and Tools for Risk-Informed Resilience Enhancement of Coastal Intermodal Freight Networks}. \textbf{Committee Member}.}{2024}

\hangingitem{Matthew Garcia: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Novel Urban Floodplain Modeling Methods for Applications in Coupling Surrogate Machine Learning Methods}. \textbf{Committee Member}.}{2023}

\hangingitem{Mia Peeples: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Modeling Flood Reduction of Nature-Based Channel Modifications in Houston, TX}. \textbf{Committee Member}.}{2023}

\hangingitem{Xiangnan Zhou: \textbf{Ph.D.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Resilience Planning for Water Distribution Systems}. \textbf{Committee Member}.}{2023}

\hangingitem{Raychel Bahnick: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Assessing Land Use Change and Subsidence Impact on Inland Flooding}. \textbf{Committee Member}.}{2022}

\hangingitem{Alyssa Graham: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Water Supply Vulnerability Testing and Robust Planning Analysis with Exploratory Modeling under Deep Uncertainty}. \textbf{Committee Member}.}{2022}

\hangingitem{Elizabeth Hoffmann: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Mapping Dynamic Watershed Response Under Increasing Development Using HEC-RAS 2D: A Case Study of the Big Creek Watershed in Fort Bend County}. \textbf{Committee Member}.}{2022}

\hangingitem{Chunshan Liu: \textbf{Ph.D.} in Statistics, Rice University. Thesis: \enquote{Bayesian Graphical Models for Multivariate Time Series}. \textbf{Committee Member}.}{2022}

\hangingitem{Xiaoyu (Toby) Li: \textbf{M.S.} in Civil and Environmental Engineering, Rice University. Thesis: \enquote{Evaluating the Effects of Project Brays Mitigation Using Unsteady HEC-RAS Hydraulic Modeling: Application to Meyerland in Houston, TX}. \textbf{Committee Member}.}{2021}

\end{alignedentrieshang}

\subsection{UNDERGRADUATE RESEARCHERS}

\textit{Year indicates graduation year.}

\medskip

\begin{alignedentrieshang}

\hangingitem{Zain Rahman: \textit{B.S. in Computer Science}, Rice University.}{2027}

\hangingitem{Kyle Olcott: \textit{B.S. in Civil and Environmental Engineering}, Rice University.}{2025}

\hangingitem{Sophia Prieto: \textit{B.S. in Statistics}, Rice University.}{2023}

\hangingitem{John Cook: \textit{B.S. in Civil and Environmental Engineering}, Rice University.}{2022}

\end{alignedentrieshang}

\subsection{TEAMS ADVISED}

\begin{alignedentrieshang}

\hangingitem{\textbf{Optimal Policy for Decentralized Wastewater Systems (DWS) while Relaxing Certainty}: Rice Computational Mathematics and Operations Research (CMOR) Senior Project.}{2024-2025}

\hangingitem{\textbf{Flood Sight | Advancing Real-Time Flood Predictions for Situational Awareness}: Rice Data to Knowledge (D2K) Lab.}{Spring 2025}

\hangingitem{\textbf{[TBD]}: Rice Data to Knowledge (D2K) Lab.}{Fall 2025}

\end{alignedentrieshang}

%% Advisee Awards
\subsection{ADVISEE AWARDS}

\begin{alignedentrieshang}

\hangingitem{\textbf{Dongwook Kim}: Karen and John Huff Graduate Fellowship in Civil and Environmental Engineering.}{2025}

\hangingitem{\textbf{Yuchen Lu}: H.W. Reeves Endowed Scholarship.}{2022}

\end{alignedentrieshang}


%% Service
\section{SERVICE ACTIVITIES}

\subsection{DEPARTMENTAL SERVICE}
\begin{alignedentrieshang}

\hangingitem{\textbf{Member}, Graduate Studies Committee.}{2024---}

\hangingitem{\textbf{Member}, Diversity, Equity, and Inclusion Committee.}{2024}

\hangingitem{\textbf{Member}, Seminar Committee.}{2023--2024}

\hangingitem{\textbf{Member}, Faculty Search Committee.}{2022--2023}

\end{alignedentrieshang}

\subsection{UNIVERSITY SERVICE}
\begin{alignedentrieshang}

\hangingitem{\textbf{Member}, Research Council. Ken Kennedy Institute.}{2024---}

\hangingitem{\textbf{Faculty Associate}. Duncan College.}{2023---}

\hangingitem{\textbf{External Search Committee Member}. Department of Earth, Environmental, and Planetary Sciences.}{2022--2023}

\end{alignedentrieshang}

\subsection{PROFESSIONAL SERVICE}
\begin{alignedentrieshang}

\hangingitem{\textbf{Committee Member}, Water and Society Newsletter Committee. American Geophysical Union.}{2024---}

\hangingitem{\textbf{Committee Member}, Environmental and Water Resources Systems (EWRS) Committee. American Society of Civil Engineers (ASCE) Environmental \& Water Resources Institute (EWRI).}{2021---}

\end{alignedentrieshang}

\subsection{PEER REVIEW}
\begin{alignedentrieshang}[2em]
  \hangingitem{\textbf{Journals:} AGU Advances; Climate Risk Management; Climatic Change; Communications Earth and Environment; Earth's Future; Energy Technology; Environmental Data Science; Environmental Research Letters; Geophysical Research Letters; Hydrology and Earth System Sciences; Joule; Journal of Applied Meteorology and Climatology; Journal of Hydrology; Journal of Water Resources Management and Planning; Oxford Journal of Development Studies; Water Resources Research; Water Security; Weather, Climate, and Society.
  }{}
  \hangingitem{\textbf{Funding Agencies:} Department of Energy (BER); National Science Foundation.
  }{}
  \hangingitem{\textbf{Other:} Electric Power Research Institute (EPRI); Texas Water Development Board (TWDB).
  }{}
\end{alignedentrieshang}
%
\subsection{SESSIONS CONVENED}
\begin{alignedentrieshang}

\hangingitem{\textbf{Co-Organizer}. \textit{Nature-Based Solutions for a Resilient Gulf Coast}. \textbf{Rice University}, Houston, TX.}{2025}

\hangingitem{\textbf{Primary Convener}. \textit{H31G - Integrating Social, Scientific, and Engineering Approaches to Identify and Address Gaps in Water Infrastructure and Household Water Security}. \textbf{American Geophysical Union Fall Meeting}, San Francisco, CA.}{2023}

\hangingitem{\textbf{Convener}. \textit{NH41C - Hybrid Modeling and Digital Twin Systems for Flood Hazard Prediction and Risk Assessment at Different Spatial Scales}. \textbf{American Geophysical Union Fall Meeting}, Washington, DC.}{2023}

\hangingitem{\textbf{Chair}. \textit{H44G -- Water and Society: Interdisciplinary Perspectives on Hydroclimatic Forecasting for Water Resources Decision Making}. \textbf{American Geophysical Union Fall Meeting}, New Orleans, LA.}{2021}

\hangingitem{\textbf{Primary Convener}. \textit{NH53 -- Emerging Needs and Approaches for Climate Services: Understanding and Developing Innovative Approaches to User-Oriented Climate Services}. \textbf{American Geophysical Union Fall Meeting}, San Francisco, CA.}{2019}

\hangingitem{\textbf{Student Organizer}. \textit{Earth and Environmental Engineering Student Research Symposium}. \textbf{Columbia University}, New York, NY.}{2018}

\hangingitem{\textbf{Student Organizer}. \textit{Earth and Environmental Engineering Student Research Symposium}. \textbf{Columbia University}, New York, NY.}{2017}

\end{alignedentrieshang}

%% Additional Experience and Training
\section{ADDITIONAL EXPERIENCE}

\begin{alignedentrieshang}

\hangingitem{\textbf{Social and Behavioral Research - Basic/Refresher} --- \textit{CITI Program}.}{2025--2028}

\hangingitem{\textbf{Strategic Program to Accelerate Researchers in Computing (SPARC) Participant} --- \textit{Natural Hazards Engineering Research Infrastructure (NHERI) DesignSafe-CI}.}{2025}

\hangingitem{\textbf{Panel Fellow} --- \textit{NSF CMMI's Game Changer Academies for Advancing Research Innovation}.}{2021}

\hangingitem{\textbf{Visiting Graduate Researcher} --- \textit{Lamontagne Research Group, Department of Civil and Environmental Engineering, Tufts University, Medford, MA}.}{2019--2020}

\hangingitem{\textbf{Graduate Research Fellow} --- \textit{Columbia Water Center, Department of Earth and Environmental Engineering, Columbia University, New York, NY}.}{2015--2020}

\hangingitem{\textbf{Summer School Participant} --- \textit{Fluid Dynamics of Sustainability and the Environment, Cambridge University, Cambridge, England}.}{2016}

\hangingitem{\textbf{Education Policy Intern} --- \textit{Elm City Communities / New Haven Housing Authority, New Haven, CT}.}{2015}

\hangingitem{\textbf{President (2014), Design Lead (2013), Member (2012, 2015)} --- \textit{Engineers Without Borders, Yale Student Chapter, New Haven, CT}.}{2012--2015}

\hangingitem{\textbf{Undergraduate Research Assistant} --- \textit{Lab of Jaehong Kim, Department of Chemical and Environmental Engineering, Yale University, New Haven, CT}.}{2014--2015}

\hangingitem{\textbf{Visiting Undergraduate Researcher} --- \textit{Water and Climate Risk Lab, Department of Hydraulic and Environmental Engineering, Universidade Federal do Ceará, Fortaleza, Brazil}.}{2014}

\hangingitem{\textbf{Mechanical Design Intern} --- \textit{Slingshot Team, DEKA Research \textbackslash\& Development, Manchester, NH}.}{2013}

\hangingitem{\textbf{Undergraduate Research Assistant} --- \textit{Lab of Jan Schroers, Department of Mechanical Engineering and Materials Science, Yale University, New Haven, CT}.}{2012}

\hangingitem{\textbf{Ikatú Agua Intern} --- \textit{Fundación Paraguaya, Asunción, Paraguay}.}{2012}

\end{alignedentrieshang}



\end{document}